---
title: "Analysis of ruler RT data"
date: 2023-10-10
---

## Purpose

This page summarizes our analysis and visualization of the reaction time data collected by Andrea Seisler in May 2023 from students at Our Lady of Victory Middle School.

```{r set-up}
library(tidyverse)
```

## Description of task

## Gathering

The data are in a Google sheet that is accessible to the psubrainlab account.

Here is a link to the data:

<https://docs.google.com/spreadsheets/d/1J-S5-kKQpHYW7L1_pqxX57zziS5IPX7ViA2MG3pGFBo/edit#gid=621964648>

First, I need to authenticate to Google.

```{r}
googledrive::drive_auth(email="psubrainlab@gmail.com")
```

Then, I download the data.

```{r}
googledrive::drive_download(
  file = "https://docs.google.com/spreadsheets/d/1J-S5-kKQpHYW7L1_pqxX57zziS5IPX7ViA2MG3pGFBo/edit?usp=sharing",
  path = "csv/rt-raw.csv",
  type = 'csv',
  overwrite = TRUE
)
```

Now, I reimport the CSV file as a data frame/tibble.

```{r}
rt <- readr::read_csv("csv/rt-raw.csv")
str(rt)
```

## Cleaning

Let's drop columns we don't need or won't use.

```{r}
rt <- rt |>
  dplyr::select(-Timestamp) |>
  dplyr::rename(
    "class" = "Class Period",
    "part_id" = "Participant ID (4 digits e.g. 7000, 7001)",
    "trial" = "Trial Number",
    "gender" = "Male or Female",
    "hand" = "Hand: Left (L) or Right (R)",
    "dom_nondom" = "Hand: D for (Dominant - the one you write with) OR N (Non-Dominant)",
    "cm" = "Distance (cm OR drop)",
    "age_range" = "age-range"
  ) |>
  dplyr::mutate(cm = as.numeric(cm))
```

## Visualization

```{r}
library(ggplot2)
rt |>
  ggplot() +
  aes(x = cm, fill = hand) +
  geom_histogram() +
  facet_grid(cols = vars(gender))
```

